---
output: 
  github_document:
    toc: yes
    toc_depth: 2
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# pigographs (under construction)

<!-- badges: start -->

<!-- badges: end -->

## Overview

This repository aims to reproduce the analysis presented in the Public
Institutions Global Observatory (PIGO): Annual Review 2025.

## Installation

```{r}
# Run the following code to ensure you have all the packages needed
find_root <- function(filename = "renv.lock") {
  path <- normalizePath(getwd(), winslash = "/", mustWork = TRUE)
  while (!file.exists(file.path(path, filename))) {
    new_path <- dirname(path)
    if (new_path == path) stop(paste("Could not find", filename, "in any parent directory"))
    path <- new_path
  }
  return(path)
}

project_root <- find_root()

renv::restore(project = project_root)
```

You can install the development version of pigographs from
[GitHub](https://github.com/) with:

```{r, eval=FALSE }
# Install devtools if you haven't already
install.packages("devtools")

# install.packages("pak")
pak::pak("WB-PIDA-Data-Science-Shop/pigographs")
```

```{r}
### Main script to build the book

```

## Instructions for Replicators

## List of Exhibits

## Requirements

### Computational Requirements

### Software Requirements

### Memory and Runtime and Storage Requirements

